Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-10 hpmoon-asoco.tex
Addressing some @JJ comments

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time. The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{Migration is performed asynchronously, as it has the advantage of being a non-blocking operation \cite{TalbiUnified2018}. The individual chosen to migrate is selected using Binary Tournament, as proposed in previous papers  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island starts the migration step, the migrated individual is sent to another randomly selected island. This makes it possible a dissemination of the modified parts of the individuals among the whole set of islands, thus avoiding a specific synchronization step to compose solutions obtained by different islands, as occurs other works \cite{Dorronsoro13superlinear}.}
 The whole parameter set is summarized in Table \ref{tab:parameters}. 
 \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these. This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}

@@

Different metrics, previously explained, have been used
to calculate the quality of the obtained PFs in each configuration. \textcolor{blue}{As HV require a reference point to be
calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it. In other words, as we are minimizing in both objectives, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs we are going to measure. HV is then
normalized respecting to that point. Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} }.  
A Kruskal-Wallis significance
test has been performed to the metrics of all runs of the
configurations, as the Kolmogorov-Smirnov test detected non-normal
distributions. The average results for each configuration are shown in
Table \ref{tab:results512} (for 512 dimensions) and Table
\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
the results of A are equivalent to the obtained by D (because
$c=0$), and when $P=16$ they are equivalent to O ($c=1$). We refer this equivalence with the word {\em Equiv-} in tables. For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.

>>>>

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time. The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{Migration is performed asynchronously, as it has the advantage of being a non-blocking operation \cite{TalbiUnified2018}. The individual chosen to migrate is selected from the subpopulation using Binary Tournament, as proposed in previous papers  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island starts the migration step, the migrated individual is sent to another randomly selected island. This makes it possible a dissemination of the modified parts of the individuals among the whole set of islands, thus avoiding a specific synchronization step to compose solutions obtained by different islands, as occurs other works \cite{Dorronsoro13superlinear}.}
 The whole parameter set is summarized in Table \ref{tab:parameters}. 
 \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these. This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}

@@

Different metrics, previously explained, have been used
to calculate the quality of the obtained PFs in each configuration. \textcolor{blue}{As HV require a reference point to be
calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it. In other words, as we are minimizing in both objectives, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs we are going to measure. HV is then
normalized respecting to that point. Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} }.  
A Kruskal-Wallis significance
test has been performed to the metrics of all runs of the
configurations, as the Kolmogorov-Smirnov test detected non-normal
distributions. The average results for each configuration are shown in
Table \ref{tab:results512} (for 512 dimensions) and Table
\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
the results of A are equivalent to the obtained by D (because
$c=0$), and when $P=16$ they are equivalent to O ($c=1$). We refer this equivalence with the word {\em Equiv-} in tables. For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.
